---
title: "betfair_login"
---

```{r echo=FALSE, message = FALSE, warning = FALSE}
library(betfaiR)
```

The `betfair_login` function is used to login to Betfair and return a session token, which is required to retrieve data from the exchange API using the different **methods**.

### usage

```{r eval=FALSE}
bf <- betfair_login(usr = username,
                    pwd = password,
                    key = api_key)
```

### arguments

param | details
------|--------
`usr` | Betfair username
`pwd` | Betfair password
`key` | Betfair API key (see Betfair [documentation](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Application+Keys) on how to get an API key)

Usernames, passwords and API Keys **SHOULD NOT** be shared, there is the danger in R that you inadvertently save these either by saving your workspace on exiting or in your .Rhistory.  The `httr` package (on which this package relies) has a very good appendix in one of its vignettes on ways to keep data like this more secure, you can read the vignette [here](https://cran.r-project.org/web/packages/httr/vignettes/api-packages.html), but the relevant section is repeated in the appendix at the bottom of this page.

### return

The function returns a list, if everything went okay (correct credentials were provided), with a class of `betfair_login`.  The list contains 3 sub lists, `usr`, `resp` and `ssoid`:

* `usr`
    - list containing the credentials you provided,
* `resp`
    - list with the response from Betfair with any errors,
* `ssoid`
    - list which includes you session token, it is this list which is to be used as the header in future requests made to the Exchange API.

You can print the object, which will display the credentials you passed into the function and any session token that was returned.

### appendix
#### username, password and API key best practices

The `betfaiR` package requires a valid Betfair username, password, and API key - see the Betfair [documentation](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Application+Keys) on how to get an API key.  The steps below show how to securely store your credentials as environment variables, preventing them from being shared inadvertently via .Rhistory or .RData files.

* Identify your home directory. Not sure? Enter `normalizePath("~/")` in the R console.
* Create a new text file.  If in RStudio, do _File > New File > Text file_
* Create the following lines:
```
BETFAIR_USR=yourusername
BETFAIR_PWD=yourpassword
BETFAIR_KEY=yourAPIkey
```
* Make sure the last line in the file is empty (if it isn't R will **silently** fail to load the file).  If you're using an editor that shows line numbers there should be four lines, 3 containing the three variables above, and a fourth empty one.
* Save the file in your home directory with the filename `.Renviron`.  If questioned, YES you do want to use a filename that begins with a dot `.`.  Note that by default [dotfiles](http://linux.about.com/cs/linux101/g/dot_file.htm) are usually hidden.  But within RStudio, the file browser will make `.Renviron` visible and therefore easy to edit in the future.
* Restart R.  `.Renviron` is processed only [at the start of an R session](http://stat.ethz.ch/R-manual/R-patched/library/base/html/Startup.html).
* Use `Sys.getenv()` to access your username, password, and API key.  For example you would use them like so with the `betfair` function:

```{r comment=""}
# load library
library(betfaiR)
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))
bf
```

FAQ:  Why define this environment variable via `.Renviron` instead of in `.bash_profile` or `.bashrc`?

Because there are many combinations of OS and ways of running R where the `.Renviron` approach _just works_ and the bash stuff does not.  When R is a child process of, say, Emacs or RStudio, you can't always count on environment variables being passed to R.  Put them in an R-specific start-up file and save yourself some grief.


<a href="https://github.com/durtal/betfaiR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
