---
title: "bf_account"
---

`bf_account` takes three arguments, your Betfair username, your password and your API key, if entered correctly then the function will return an environment with a few methods for retrieving data and performing actions on your Betfair account.

```{r echo=FALSE, message=FALSE}
library(betfaiR)
acc <- bf_account(usr = Sys.getenv("BETFAIR_USR"),
                  pwd = Sys.getenv("BETFAIR_PWD"),
                  key = Sys.getenv("BETFAIR_KEY"))
```

### usage

```{r eval=FALSE, comment=""}
acc <- bf_account(usr = username,
                 pwd = password,
                 key = api_key)
```

If using the `account` method found in the [`betfair`](betfair.html) environment, then only the password is required, which is checked against the previously entered password.

### arguments

param | details
------|--------
`usr` | Betfair username
`pwd` | Betfair password
`key` | Betfair API key (see Betfair [documentation](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Application+Keys) on how to get an API key)

### return

The function returns an environment (stored as `acc` in the usage section) with a few methods for retrieving account data.  To view the available methods you can print the environment.

```{r comment=""}
acc
```

method | details
-------|--------
`details` | account details, such as first name, last name, etc
`funds` | account funds, available to bet balance, exposure, points balance, etc
`statement` | account statement, returns a list with transactions, can be filtered according to date, wallet, number of records, etc.
`transfer` | transfer funds from one wallet to another

I won't show examples of these functions as it could accidently involve me sharing some sensitive data, but they are simple enough.  `funds` and `details` require no parameters to be entered, `transfer` requires `from`, `to` and `amount` to be entered (from and to are wallets, UK and AUSTRALIAN).  `statement` can be left blank also, but it's probably best to see the help pages `?statement`
