---
title: "bf_helpers"
---

`bf_helpers` is an environment which contains a number of small helper functions used in conjunction with various methods, these functions are listed below:

<hr>

## `limitOrder`

This helper function is to be used with the [`placedOrders`](placedOrders.html) method when an orderType is **LIMIT**, to help construct the conditions of a bet.

### usage

```{r eval=FALSE}
bf_helpers$limitOrder(size = 2
                      price = 1.01,
                      persistenceType = "LAPSE")
```

### arguments

param | details
------|--------
size | the size of the best. **NB.** for a market type of **EACH_WAY** the total stake is 2 \* size.
price | the limit price
persistenceType | what to do with the order when the market goes in-play.  **LAPSE** (default) - lapse the order when the market goes in play.  **PERSIST** - persist the order in play, the bet will be placed automatically into the in play market at the start of the event.  **MARKET_ON_CLOSE** - put the order into the auction (SP) at in-play.

<hr>

## `limitOnCloseOrder`

This helper function is to be used with the [`placeOrders`](placeOrders.html) method when an orderType is **LIMIT_ON_CLOSE**, to help construct the conditions of a bet.

### usage

```{r eval=FALSE}
bf_helpers$limitOnCloseOrder(size = 2,
                             price = 1.01)
```

### arguments

param | details
------|--------
size | the size of the bet. **NB.** for a market type of **EACH_WAY** the total stake is 2 \* size.
price | the limit price

<hr>

## `cancel_inst`

This helper function is to be used with the [`cancelOrders`](cancelOrders.html) method, to help cancel individual orders using their betIds.

### usage

```{r eval=FALSE}
bf_helpers$cancel_inst(betId = "unique_bet_id",
                       size = 1.02)
```

### arguments

param | details
------|---------
betId | the unique betId, returned when the bet was placed, these can also be retrieved by the [`currentOrders`](currentOrders.html) method.
size | reduction size

<hr>

## `replace_inst`

This helper function is to be used with the [`cancelOrders`](updateOrders.html) method, to help replace individual orders using their betIds.

### usage

```{r eval=FALSE}
bf_helpers$replace_inst(betId = "unique_bet_id",
                        newPrice = 1.10)
```

### arguments

param | details
------|--------
betId | the unique betId, returned when the bet was placed, these can also be retrieved by the [`currentOrders`](currentOrders.html) method.
newPrice | new price to strike the bet

<hr>

## `update_inst`

This helper function is to be used with the [`updateOrders`](updateOrders.html) method, to help replace individual orders using their betId with new instructions for what to do when the market goes in-play.

### usage

```{r eval=FALSE}
bf_helpers$update_inst(betId = "unique_bet_id",
                       persistenceType = "PERSIST")
```

### arguments

param | details
------|--------
betId | the unique betId, returned when the bet was placed, these can also be retrieved by the [`currentOrders`](currentOrders.html) method.
persistenceType | new persistenceType, what to do when the market goes in-play.  **LAPSE** - lapse the order when the market is turned in-play.  **PERSIST** - persist the order in-play, the bet will be placed automatically into the in-play market at the start of the event.  **MARKET_ON_CLOSE** - put the order into the auction (SP) at turn in-play.

<hr>

The following functions are used within various methods for preparing a correctly formatted request.

## `cancel`

This helper function prepares the request for the [`cancelOrders`](cancelOrders.html) method, the usage is the same as that method, this function just converts those params into a format ready to be sent via a request:

### usage

```{r eval=FALSE}
bf_helpers$cancel(..., marketId)
```

### params

param | details
------|--------
`...` | specific details about bets to cancel, use `cancel_inst` (see [above](bf_helpers.html#cancel_inst)) function to target specific bets via their id
`marketId` | the unique id for the market in which bets should be cancelled

<hr>

## `prepare`

This helper function is used with the [`placeOrders`](placeOrders.html) method to place orders in specific markets, it uses another couple of helper functions, `limitOrder` and `limitOnCloseOrder`.

### usage

```{r eval=FALSE}
bf_helpers$(marketId,
            selectionId,
            orderType = "LIMIT",
            handicap = "0",
            side = "BACK",
            limitOrder = bf_helpers$limitOrder(),
            limitOnCloseOrder = bf_helpers$limitOnCloseOrder()
            marketOnCloseOrder = list())
```

### params

param | details
------|--------
`marketId` | unique market id into which the bet will be placed
`selectionId` | the unique id for the selection in the market, this will be a horse, a team, etc, these ids can be found using the [`marketCatalogue`](methods_marketCatalogue.html) and [`marketBook`](methods_marketBook.html) methods
`orderType` | the type of order, **LIMIT** - a normal exchange order for immediate execution, **LIMIT\_ON\_CLOSE** - limit oder for the auction (SP bet with a price limit), **MARKET\_ON\_CLOSE** - market order for the auction, SP bet regardless of price.
`handicap` | for ASIAN handicap markets (I believe!), default is 0
`side` | **BACK** or **LAY**
`limitOrder` | list with details of the bet, required if `orderType` is **LIMIT**, use [`limitOrder`](orders.html#limitorder) to help construct correct list
`limitOnCloseOrder` | list with details of the bet, required if `orderType` is **LIMIT\_ON\_CLOSE**, use [`limitOnCloseOrder`](orders.html#limitoncloseorder) to help construct correct list
`marketOnCloseOrder` | single number, the size of your bet to be placed at Betfairs SP.

<hr>

## `cleared`

This helper function is used by the [`clearedOrders`](clearedOrders.html) method to build a request for retrieving data about orders that have been settled.

### usage

```{r eval=FALSE}
bf_helpers$cleared(betStatus = "SETTLED",
                   eventTypeIds = NULL,
                   eventIds = NULL,
                   marketIds = NULL,
                   runnerIds = NULL,
                   betIds = NULL,
                   side = NULL,
                   from = NULL,
                   to = NULL)
```

### arguments

param | details
------|--------
betStatus | filter based on how the bet was settled, default is **SETTLED**, other options include, **VOIDED**, **LAPSED**, or **CANCELLED**
eventTypeIds | filter based on sport, see [`eventTypes`](methods_eventTypes.html) method for the ids of various sports
eventIds | filter based on events, see [`events`](methods_events.html) method for the various event ids
marketIds | filter based on marketIds
runnerIds | filter based on specific runners
betIds | unique bets
side | **BACK** or **LAY**
from | filter according to date, format should be in yyyy-mm-dd
to | filter according to date, format should be in yyyy-mm-dd

<hr>

## `current`

This helper function is used by the [`currentOrders`](currentOrders.html) method to build a request for retrieving data about any current orders.

### usage

```{r eval=FALSE}
bf_helpers$current(betId = NULL,
                   marketId = NULL,
                   orderProjection = "ALL",
                   from = NULL,
                   to = NULL,
                   orderBy = NULL,
                   sort = NULL,
                   fromRecord = NULL,
                   count = NULL)
```

### arguments

param | details
------|--------
betId | unique bet id
marketId | unique market id
orderProjection | default of **ALL**, returns all unsettled positions, matched or partially matched.  **EXECUTABLE** to filter for orders with a portion remaining.  **EXECUTION_COMPLETE** for orders which have been filled.  See [betting enums](betting_enums.html#orderprojection) for more details.
from | filter according to date, format should be in yyyy-mm-dd
to | filter according to date, format should be in yyyy-mm-dd
orderBy | how to order orders, default is to order them by when they were placed, see [betting enums](betting_enums.html#orderby) for more details
sort | how to sort the results, see [betting enums](betting_enums.html#sortdir) for more details
fromRecord | specifies the first record to be retured, records start at index zero (not one)
count | specifies how many records are retured from the index position set by `fromRecord`, there is a limit of 1000.


<a href="https://github.com/durtal/betfaiR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
