---
title: "cancelOrders"
---

**This function allows bets to be cancelled which were placed via [`placeOrders`](placeOrders.html)**

Having logged in using the [`betfair`](betfair.html) function and placed any number of bets using the [`placeOrders`](placeOrders.html) function, you may wish to cancel some or all of those bets, the `cancelOrders` method can help.

### usage

```{r eval=FALSE}
bf$cancelOrders(...,
                marketId = NA)
```

### arguments

param | details
------|--------
`...` | specific details about bets to cancel, use `cancelInstructions` (see [below](cancelOrders.html#cancelinstruction)) function to target specific bets via their id
`marketId` | the unique id for the market in which bets should be cancelled

### details

To cancel all unmatched or partially matched bets leave the function params empty, like so:

```{r eval=FALSE}
bf$cancelOrders()
```

If you wish to target a specific market then add the relevant marketId to the marketId argument, and to target multiple bets in the same market use [`cancelInstruction`](cancelOrders.html#cancelinstruction), like so:

```{r eval=FALSE}
bf$cancelOrders(cancelInstruction(betId = bet_id_1,
                                  size = 20),
                cancelInstruction(betId = bet_id_4,
                                  size = 10),
                marketId = marketId)
```

### return

The function should return details about whether the cancellation was successful or not, and if you entered any specific instructions, via the `marketId` and `...` (using the `cancelInstruction` function) params then the response should contain data about the bets cancelled, and size of stake returned.  The response can be passed to `print` and `summary` for easy to interpret results.

## cancelInstruction

The `cancelInstruction` function helps construct instructions by which to cancel an existing bet, one or both parameters should be entered

### usage

```{r eval=FALSE}
cancelInstructions(betId = NA,
                   size = NA)
```

### arguments

param | details
------|---------
`betId` | the unique bet Id
`size` | the amount of the bet to cancel
