---
title: "login and session"
---

The environment returned by the [`betfair`](betfair.html) function contains a number of methods for querying the Betfair API-NG.  Two important methods that may require attention are `session` and `login`.

So login as shown below...

```{r eval=FALSE}
library(betfaiR)
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))
```

If everything went smoothly Betfair will have issued you with a session token.  To check this is the case, use the `session` method:

```{r eval=FALSE}
bf$session()
```

The above will print your current session token, if you have been assigned one.  If you entered invalid credentials, then the `login` method allows you to login again with valid credentials:

```{r eval=FALSE}
bf$login(usr = username, pwd = password, key = API_key)
```

You do not need to write to a new object, or overwrite the environment you initially created (in the case above the `bf` object), the `login` method will simply overwrite the credentials in the `bf` environment.
