---
title: "marketFilter"
---

```{r echo=FALSE, message = FALSE, warning = FALSE}
library(betfaiR)
```
The `marketFilter` function is used to build an object to filter and select the desired markets.  This function is used in a number of methods, including [`competitions`](methods_competitions.html), [`countries`](methods_countries.html), [`events`](methods_events.html), [`eventTypes`](methods_eventTypes.html), [`marketCatalogue`](methods_marketCatalogue.html), and [`marketTypes`](methods_marketTypes.html).

### usage

See examples.

```{r eval=FALSE}
m <- marketFilter(bspOnly = NULL, competitionIds = NULL, eventIds = NULL, eventTypeIds = NULL,
                  exchangeIds = NULL, inPlayOnly = NULL, marketBettingTypes = NULL,
                  marketCountries = NULL, marketIds = NULL, from = NULL, to = NULL,
                  marketTypeCodes = NULL, textQuery = NULL, turnInPlayEnabled = NULL,
                  venues = NULL, withOrders = NULL)
```

### arguments

param | type | details | example
------|------|---------|--------
`bspOnly` | `boolean` | restrict to BSP (Betfair Starting Price) markets only `TRUE`, or non-BSP markets `FALSE`.  If not specified then returns both BSP and non-BSP markets | `TRUE`
`competitionIds` | `string` | restrict markets by the competitions associated with the competition id | `"123456"`
`eventIds` | `string` | restrict markets by the event id | `"767956"`
`eventTypeIds` | `numeric` | restrict markets by event type, ie. Football, Hockey, Horse Racing, etc | `"1"`
`exchangeIds` | `string` | restrict markets by the exchange where the market operates.  As of Jun 11, 2015, **not available** |
`inPlayOnly` | `boolean` | restrict to markets that are currently in play `TRUE`, or not currently in play `FALSE`.  If not specified then returns both. | `TRUE`
`marketBettingTypes` | `string` | restrict to markets that match the betting type or the market, ie. Odds, Asian Handicap Singles, Asian Handicap Doubles.  See section **marketBettingTypes** in [BettingEnums](betting_enums.html) or the relevant section of Betfair [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Enums#MarketBettingType) | `"ODDS"`
`marketCountries` | `string` | restrict to markets that are in the specified country or countries | `"GB"`
`marketIds` | `numeric` | restrict to markets by market Id | `"1.2345678"`
`from` | `string` | start time **after** specified date, format date as "YYYY-MM-DD" or with a time "YYYY-MM-DD 00:00:00" | `"2015-09-23"`
`to` | `string` | start time **before** specified date, format date as "YYYY-MM-DD" or with a time "YYYY-MM-DD 00:00:00" | `"2015-09-24"`
`marketTypeCodes` | `numeric` | restrict to markets that match the type of the market, ie. MATCH_ODDS, HALF_TIME_SCORE.  You should use this instead of relying on the market name as the market type codes are the same in all locales. | `"MATCH_ODDS"`
`textQuery` | `string` | restrict markets by any text associated with the market such as Name, Event, Competition, etc.  You can include a wildcard (\*) character, as long as it is not the first character | `"Capital One Cup"`
`turnInPlayEnabled` | `boolean` | restrict to markets that will turn in play `TRUE`, or will not turn in play `FALSE`.  If not specified returns both | `TRUE`
`venues` | `string` | restrict markets by the venue.  Currently, as of Jun 11, 2015, only Horse Racing and Greyhound markets have venues. | `"Haydock"`
`withOrders` | `string` | restrict to markets that you have one or more orders in place, see section **OrderStatus** in [BettingEnums](betting_enums.html) or the relevant section of Betfair [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Enums#OrderStatus) | `"EXECUTABLE"`

### examples

```{r comment="", tidy=TRUE}
library(betfaiR)
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# build filter object, for all football markets
obj <- marketFilter(eventTypeIds = 1)
# use obj in query
res <- bf$competitions(filter = obj)
head(res)

# or use marketFilter inside a method
res <- bf$competitions(filter = marketFilter(eventTypeIds = 1, marketCountries = "GB"))
head(res)
```

<a href="https://github.com/durtal/betfaiR" class="github-corner"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#d9230f; color:#fcfcfc; position: absolute; top: 0; border: 0; right: 0;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
