---
title: "marketFilter"
---

```{r echo=FALSE, message = FALSE, warning = FALSE}
library(betfaiR)
```
The `marketFilter` function is used to build an object to filter and select the desired markets.  This function is used in a number of methods, including [`competitions`](methods_competitions.html), [`countries`](methods_countries.html), [`events`](methods_events.html), [`eventTypes`](methods_eventTypes.html), [`marketCatalogue`](methods_marketCatalogue.html), and [`marketTypes`](methods_marketTypes.html).

### usage

See examples.

```{r eval=FALSE}
m <- marketFilter(bspOnly = NULL, competitionIds = NULL, eventIds = NULL, eventTypeIds = NULL,
                  exchangeIds = NULL, inPlayOnly = NULL, marketBettingTypes = NULL,
                  marketCountries = NULL, marketIds = NULL, from = NULL, to = NULL,
                  marketTypeCodes = NULL, textQuery = NULL, turnInPlayEnabled = NULL,
                  venues = NULL, withOrders = NULL)
```

### arguments

param | type | details | example
------|------|---------|--------
`bspOnly` | `boolean` | restrict to BSP (Betfair Starting Price) markets only `TRUE`, or non-BSP markets `FALSE`.  If not specified then returns both BSP and non-BSP markets | `TRUE`
`competitionIds` | `string` | restrict markets by the competitions associated with the competition id | `"123456"`
`eventIds` | `string` | restrict markets by the event id | `"767956"`
`eventTypeIds` | `numeric` | restrict markets by event type, ie. Football, Hockey, Horse Racing, etc | `"1"`
`exchangeIds` | `string` | restrict markets by the exchange where the market operates.  As of Jun 11, 2015, **not available** |
`inPlayOnly` | `boolean` | restrict to markets that are currently in play `TRUE`, or not currently in play `FALSE`.  If not specified then returns both. | `TRUE`
`marketBettingTypes` | `string` | restrict to markets that match the betting type or the market, ie. Odds, Asian Handicap Singles, Asian Handicap Doubles.  See section **marketBettingTypes** in [BettingEnums](betting_enums.html) or the relevant section of Betfair [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Enums#MarketBettingType) | `"ODDS"`
`marketCountries` | `string` | restrict to markets that are in the specified country or countries | `"GB"`
`marketIds` | `numeric` | restrict to markets by market Id | `"1.2345678"`
`from` | `string` | start time **after** specified date, format date as "YYYY-MM-DD" or with a time "YYYY-MM-DD 00:00:00" | `"2015-09-23"`
`to` | `string` | start time **before** specified date, format date as "YYYY-MM-DD" or with a time "YYYY-MM-DD 00:00:00" | `"2015-09-24"`
`marketTypeCodes` | `numeric` | restrict to markets that match the type of the market, ie. MATCH_ODDS, HALF_TIME_SCORE.  You should use this instead of relying on the market name as the market type codes are the same in all locales. | `"MATCH_ODDS"`
`textQuery` | `string` | restrict markets by any text associated with the market such as Name, Event, Competition, etc.  You can include a wildcard (\*) character, as long as it is not the first character | `"Capital One Cup"`
`turnInPlayEnabled` | `boolean` | restrict to markets that will turn in play `TRUE`, or will not turn in play `FALSE`.  If not specified returns both | `TRUE`
`venues` | `string` | restrict markets by the venue.  Currently, as of Jun 11, 2015, only Horse Racing and Greyhound markets have venues. | `"Haydock"`
`withOrders` | `string` | restrict to markets that you have one or more orders in place, see section **OrderStatus** in [BettingEnums](betting_enums.html) or the relevant section of Betfair [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Enums#OrderStatus) | `"EXECUTABLE"`

### examples

```{r}
library(betfaiR)
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# build filter object, for all football markets
obj <- marketFilter(eventTypeIds = 1)
# use obj in query
res <- bf$competitions(filter = obj)
head(res)

# or use marketFilter inside a method
res <- bf$competitions(filter = marketFilter(eventTypeIds = 1, marketCountries = "GB"))
head(res)
```
