---
title: "eventTypes"
---

Having logged in using the [`betfair`](betfair.html) function, the environment contains the `eventTypes` method.  This method can be used to get the number of events that belong to an event type, eg. Football, Horse Racing, etc.

### usage

```{r eval=FALSE}
bf$eventTypes(filter = marketFilter())
```

### arguments

param | details
------|---------
`filter` | select desired markets, see [marketFilter](marketFilter.html) for various parameters to filter by, or the relevant [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Type+Definitions#BettingTypeDefinitions-MarketFilter) on Betfair.  If nothing is entered, **all** competitions are returned

### return

The function returns a dataframe of eventTypes, with data about the number of markets.

variable | details
---------|--------
`eventType_id` | the eventType id
`eventType_name` | the eventType name (eg. Football, Horse Racing)
`marketCount` | number of markets associated with this country

### examples

```{r}
library(betfaiR)
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# return all countries
tmp <- bf$eventTypes()
head(tmp)

# return all horse racing events
tmp <- bf$eventTypes(filter = marketFilter(marketCountries = "GB"))
head(tmp)

# return all horse racing events whose start date is beyond next week
tmp <- bf$eventTypes(filter = marketFilter(eventTypeIds = 7, from = Sys.Date() + 7))
head(tmp)
```
