---
title: "events"
---

Having logged in using the [`betfair`](betfair.html) function, the environment contains the `events` method.  This method can be used to get events and the number of markets for each event, when the event start, as well as other data that may be of interest.

### usage

```{r eval=FALSE}
bf$events(filter = marketFilter())
```

### arguments

param | details
------|---------
`filter` | select desired markets, see [marketFilter](marketFilter.html) for various parameters to filter by, or the relevant [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Type+Definitions#BettingTypeDefinitions-MarketFilter) on Betfair.  If nothing is entered, **all** events are returned

### return

The function returns a dataframe of events (eg. Manchester United vs Arsenal), with data about the number of markets, start time, etc, a full list below:

variable | details
---------|--------
`event_id` | the event id
`event_name` | the event name (eg. Manchester United vs Arsenal)
`event_countryCode` | the ISO-2 code, ISO-2 codes are available on [wiki](https://en.wikipedia.org/wiki/ISO_3166-1_alpha-2), examples include _GB_, _IE_, _US_, etc
`event_timezone` | the timezone in which the event is happening
`event_venue` | the event venue (if applicable)
`event_openDate` | the scheduled start of the event (format "YYYY-MM-DDT00:00:00.000Z")
`marketCount` | number of markets associated with this country

### examples

```{r}
library(betfaiR)
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# return all countries
tmp <- bf$events()
head(tmp)

# return all horse racing events
tmp <- bf$events(filter = marketFilter(eventTypeIds = 7))
head(tmp)

# return all horse racing events whose start date is beyond next week
tmp <- bf$events(filter = marketFilter(eventTypeIds = 7, from = Sys.Date() + 7))
head(tmp)
```
