---
title: "marketTypes"
---

Having logged in using the [`betfair`](betfair.html) function, the environment contains the `marketTypes` method.  This method can be used to get the various types of markets (eg. WINNER, HANDICAP, OVER_UNDER_25, etc), and the number of markets.

### usage

```{r eval=FALSE}
bf$marketTypes(filter = marketFilter())
```

### arguments

param | details
------|---------
`filter` | select desired markets, see [marketFilter](marketFilter.html) for various parameters to filter by, or the relevant [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Type+Definitions#BettingTypeDefinitions-MarketFilter) on Betfair.  If nothing is entered, **all** marketTypes are returned

### return

The function returns a dataframe of market Types and the number of markets associated with that type.

variable | details
---------|--------
`marketType` | the type of market (eg. WINNER, HANDICAP, OVER_UNDER_25)
`marketCount` | the number of markets currently available associated with this market type

### examples

```{r eval=FALSE}
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# return all countries
bf$marketTypes()

# return all horse racing events
bf$marketTypes(filter = marketFilter(eventTypeIds = 7))

# return all horse racing events whose start date is beyond next week
bf$marketTypes(filter = marketFilter(eventTypeIds = 7, from = Sys.Date() + 7))
```
