---
title: "countries"
---

Having logged in using the [`betfair`](betfair.html) function, the environment contains the `countries` method.  This method can be used to get countries and the number of markets in each, these two letter country codes can then be used to help filter and find desired markets.

### usage

```{r eval=FALSE}
bf$countries(filter = marketFilter())
```

### arguments

param | details
------|---------
`filter` | select desired markets, see [marketFilter](marketFilter.html) for various parameters to filter by, or the relevant [help pages](https://api.developer.betfair.com/services/webapps/docs/display/1smk3cen4v3lu3yomq5qye0ni/Betting+Type+Definitions#BettingTypeDefinitions-MarketFilter) on Betfair.  If nothing is entered, **all** competitions are returned

### return

The function returns a dataframe of countries with available markets, and the number of markets:

variable | details
---------|--------
`countryCode` | the ISO-2 code, ISO-2 codes are available on [wiki](https://en.wikipedia.org/wiki/ISO_3166-1_alpha-2), examples include _GB_, _IE_, _US_, etc
`marketCount` | number of markets associated with this country

### examples

```{r eval=FALSE}
# login
bf <- betfair(usr = Sys.getenv("BETFAIR_USR"),
              pwd = Sys.getenv("BETFAIR_PWD"),
              key = Sys.getenv("BETFAIR_KEY"))

# return all countries
bf$countries()

# return all countries with horse racing markets
bf$countries(filter = marketFilter(eventTypeIds = 7))

```
