---
title: "orders"
---

## limitOrder

The `limitOrder` function helps construct a bet order in the correct format.

### usage

```{r eval=FALSE}
limitOrder(size = 2,
           price = NULL,
           persistenceType = "LAPSE")
```

### arguments

param | details
------|--------
`size` | the size of the bet, **NB**, for a market type of **EACH\_WAY** the total stake is 2*size
`price` | the limit price, the price you wish to place your bet
`persistenceType` | what to do with the order at turn in play, three choices.  **LAPSE** - lapse the order when the market goes in play (ie. cancel bet); **PERSIST** - persist the order at in-play, the bet will be placed automatically into the in-play market at the start of the event; **MARKET\_ON\_CLOSE** - put the order into the auction (SP) at turn in-play

### returns

A simple list

## limitOnCloseOrder

The `limitOnCloseOrder` function helps construct a bet order in the correct format.

### usage

```{r eval=FALSE}
limitOnCloseOrder(size = 2,
                  price = NULL)
```

### arguments

param | details
------|--------
`size` | the size of the bet, **NB**, for a market type of **EACH\_WAY** the total stake is 2*size
`price` | the limit price, the price you wish to place your bet

### returns

A simple list

## betfaiR:::prepare_order

The `prepare_order` function helps contruct a bet, it is used inside the [`placeOrders`](placeOrders.html) function.

### usage

```{r eval=FALSE}
prepare_order(marketId,
              selectionId,
              orderType = "LIMIT",
              handicap = "0",
              side = "BACK",
              limitOrder = limitOrder(),
              limitOnCloseOrder = limitOnCloseOrder(),
              marketOnCloseOrder = list())
```

### arguments

param | details
------|--------
`marketId` | unique market id into which the bet will be placed
`selectionId` | the unique id for the selection in the market, this will be a horse, a team, etc, these ids can be found using the [`marketCatalogue`](methods_marketCatalogue.html) and [`marketBook`](methods_marketBook.html) methods
`orderType` | the type of order, **LIMIT** - a normal exchange order for immediate execution, **LIMIT\_ON\_CLOSE** - limit oder for the auction (SP bet with a price limit), **MARKET\_ON\_CLOSE** - market order for the auction, SP bet regardless of price.
`handicap` | for ASIAN handicap markets (I believe!), default is 0
`side` | **BACK** or **LAY**
`limitOrder` | list with details of the bet, required if `orderType` is **LIMIT**, use [`limitOrder`](orders.html#limitOrder) to help construct correct list
`limitOnCloseOrder` | list with details of the bet, required if `orderType` is **LIMIT\_ON\_CLOSE**, use [`limitOnCloseOrder`](orders.html#limitOnCloseOrder) to help construct correct list
`marketOnCloseOrder` | single number, the size of your bet to be placed at Betfairs SP.

### return

A list with details about the bet.
